### 2024-03-18 ms.qmd
Updates

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

```{r, tbl-data}
#| label: tbl-data
#| tbl-cap: "Estimates of learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"
############################## CREATING BIG DF FOR TABLE ##############################
# Building the vectors for titles of rows and columns
specie <- c("L. delicata", "L. guichenoti")
groups <- c("Red", "Blue")
treatments <- c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")
values <- c("Mean", "95% CI", "p-value")
# Building the vectors for estimated means, co.intervals(95%), and p-values for the slopes obtained from posteriors. p-values are obtained using pmcmc function (see func.R), assuming a two-tailed test that testes the hypothesis that the value (slopes in this case) is 0.
# First call the estimates
estimates <- list(
  dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot, 
  dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot, 
  gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot, 
  gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot
)
# Then get the mean, co.intervals(95%), and p-values
l_mean <- format_dec(sapply(estimates, mean), 3)
l_interval_025 <- format_dec(sapply(estimates, function(x) quantile(x,0.025)), 3)
l_interval_975 <- format_dec(sapply(estimates, function(x) quantile(x,0.975)), 3)
l_intervals <- paste(l_interval_025, l_interval_975, sep = " , ")
l_pvalue <- format_p(sapply(estimates, pmcmc), 3)
# Building the df
df <- data.frame(
  Specie = rep(specie, each = length(groups) * length(treatments)),
  Group = rep(rep(groups, each = length(treatments)), times = length(specie)),
  Treatment = rep(rep(treatments, each = 1), times = length(groups) * length(specie)),
  Mean = rep(l_mean, each = 1),
  CI = rep(l_intervals, each = 1),
  PValue = rep(l_pvalue, each = 1)
)
write.csv(df, file= "./output/Checking/df.csv")
############################## ADDING SAMPLE SIZE TO DF FOR TABLE ##############################
# Make n_list into a df
n_df <- as.data.frame(do.call(rbind, n_list)) %>%
  rename("n" = V1) %>%
  rownames_to_column("model") %>%
  separate(model, into = c("Specie", "Group", "cort", "temp"), sep = "_") %>%
  unite("Treatment", c("cort", "temp"), sep = "-") %>%
                  labels = c(delicata = "L. delicata", guichenoti = "L. guichenoti")),
        Treatment = factor(Treatment,
                   levels = c("CORT-Cold", "Control-Cold", "CORT-Hot","Control-Hot")))
# Merge both dfs, put sample size together with the treatment, and organize the new df to make it look like the table
table_data <- merge(df, n_df) %>%
  rename('p-value' = 'PValue', '95% CI' = 'CI') %>% #Change the names of the columns for the table
  select(Specie, Group, Treatment, Mean, `95% CI`, `p-value`, n) %>% #To order the columns in the way I want for the table
                  levels = c("L. delicata", "L. guichenoti")),
        Group = factor(Group,
                  levels = c("Red", "Blue")),
        Treatment = factor(Treatment, 
                  levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")))%>%
  arrange(Specie, Group, Treatment) %>% # To arrange the rows the way I want
  unite("Treatment", c("Treatment", "n"), sep = " (n = ") %>%
  mutate(Treatment = paste0(Treatment, ")"))
write.csv(table_data, file= "./output/Checking/table_data.csv")
############################## MAKING THE TABLE ##############################
## Table format
set_flextable_defaults(
 font.family = "Times New Roman",
 fint.size = 10)
# Split the table_data df by task
real_table <- flextable(table_data) %>%
    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%
    set_header_labels(Mean = "Mean",
                      `95% CI` = "95% CI",
                      `p-value` = "p-value",
                      Mean_Reversal = "Mean",
                      `95% CI_Reversal` = "95% CI",
                      `p-value_Reversal` = "p-value") %>%
    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
    hline(i = c(4,12), j = c(2:6), part = "body") %>% # To make some horizontal lines
    hline(i = c(8), j = c(1:6), part = "body") %>% # To make some horizontal lines
real_table

Results of the are summarized in @tbl-data and @fig-results. On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red' for _L. delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`). However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes. As such, we analysed the between treatments differences for each group separately.  
For those individuals assigned to group 'Red', we did not find any significant differences between treatments neither for _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_p(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_p(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_p(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_p(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @fig-results), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_p(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_p(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_p(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_p(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @fig-results). However, in both species the slope in the 'CORTCold' treatments seems bigger than the rest for group 'Red'. When groups were pooled by incubation temperature, slopes from individuals incubated at 23ºC were on average bigger in both species, but the difference was not significant (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_p(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_p(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`). CORT also lead to higher slopes in both species, but the differences were not significant (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_p(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_p(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`). We also did not find any significant differences when we compared the estimated slopes between species (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_p(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).

@@

The results for 'Blue' individuals were similar. We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_p(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_p(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_p(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_p(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @fig-results), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_p(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_p(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_p(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_p(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @fig-results). However, here the estimated slopes from those incubated at higher temperatures seem to be bigger on average, although the difference was not significant (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`, p-value = `r format_p(pmcmc((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`, p-value = `r format_p(pmcmc((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`). Also, 'Control' _L. delicata_ seem to have slightly higher estimated slopes than on average ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)`, p-value = `r format_p(pmcmc((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)` ) while in _L. guichenoti_ is the opposite ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`, p-value = `r format_p(pmcmc((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`); nevertheless, the differences found were not significant in any case. Finally, we found that learning slopes estimated for _L. guichenoti_ assigned to group 'Blue' were marginally higher than those from _L. delicata_ (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_p(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).

@@

On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L. delicata_: mean Prob choice = `r format_dec(mean((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_dbCORTCold + probright_dbControlCold + probright_dbCORTHot + probright_dbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L. guichenoti_: mean Prob choice = `r format_dec(mean((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_gbCORTCold + probright_gbControlCold + probright_gbCORTHot + probright_gbControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L. delicata_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L. guichenoti_: mean Prob choice = `r format_dec(mean((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), 3)`, p-value = `r format_p(pmcmc(((probright_drCORTCold + probright_drControlCold + probright_drCORTHot + probright_drControlHot)/4), null = 0.33, twotail = FALSE, dir=">"), 3)`).

>>>>

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @fig_deli and @fig-guich.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L. delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`). However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes. As such, we analysed the between treatments differences for each group separately.

For those _L. delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (**FIG**). Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (**FIG**).

```{r, fig-deli}
```

In _L. guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (**FIG**); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (**FIG**).

```{r, fig-guich}
```

Finally, we also did not find any significant differences when we compared the estimated slopes between species for 'Red' group(_L. delicata_ mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot), 0.975), 3)`]; _L. guichenoti_ mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot), 0.975), 3)`]; _L. delicata_ - _L. guichenoti_ = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_CORTCold, dar_ControlCold, dar_CORTHot, dar_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTHot, gar_ControlHot)), 3)`) or the 'Blue' one (_L. delicata_ mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; _L. guichenoti_ mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; _L. delicata_ - _L. guichenoti_ = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot))), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`).

@@

@@

On average, we found that, for both species, the proportion of correct choices in the first trial was significantly above chance when the correct feeder was blue (_L. delicata_: mean Prob choice = `r format_dec(mean(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_dbCORTCold, probright_dbControlCold, probright_dbCORTHot, probright_dbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L. guichenoti_: mean Prob choice = `r format_dec(mean(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_gbCORTCold, probright_gbControlCold, probright_gbCORTHot, probright_gbControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`), but not when it was red (_L. delicata_: mean Prob choice = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`; _L. guichenoti_: mean Prob choice = `r format_dec(mean(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(probright_drCORTCold, probright_drControlCold, probright_drCORTHot, probright_drControlHot), null = 0.33, twotail = FALSE, dir=">"), 3)`).
